---
title: "HW5"
author: "Matt Untalan"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


### Due date

Due: November 16 at 11:59pm. 

### Points

| Problem         | Points    |
|:--------------- |:--------- |
| Problem 0       | 20        |
| Problem 1       | --        |
| Problem 2       | 40        |
| Problem 3       | 40        |
| Optional survey | No points |


### Problem 0

This "problem" focuses on structure of your submission, especially the use git and GitHub for reproducibility, R Projects to organize your work, R Markdown to write reproducible reports, relative paths to load data from local files, and reasonable naming structures for your files. This was not prepared as a GitHub repo.

```{r load_libraries}
library(tidyverse)
```

## Problem 2

The raw dataset includes 12 variables: the individual's unique id number; homicide report date (listed as yyyymmdd); victim information such as first and last name, age, and sex; location of the homicide including coordinates; and status of the case.

Create city_state variable and classify current disposition variable into solved/unsolved
```{r status}
homicide = 
  read_csv("prob2_data/homicide-data.csv", na = c("", "Unknown")) %>%
  mutate(
    city_state = paste(city, state, sep=","),
    status = case_when(
        disposition == "Closed by arrest" ~ "Solved",
        disposition == "Closed without arrest" ~ "Unsolved",
        disposition == "Open/No arrest" ~ "Unsolved"))
```

Unsolved Cases for Baltimore
```{r baltimore}
balt = 
  homicide %>%
  filter(city_state == "Baltimore,MD")

balt_sum =
  balt %>%
  summarize(
    unsolved = sum(status == "Unsolved"),
    n = n()
  )

balt_prop = 
  prop.test(
    x =
      balt_sum %>%
      pull(unsolved),
    n =
      balt_sum %>%
      pull(n)
  )

broom::tidy(balt_prop) %>%
  select(estimate, conf.low, conf.high) %>%
  knitr::kable()
```